### 2015-02-08 src/paper4/p4_discussion.tex
Minor updates

\subsection{Relation to previous studies}

@@

% Relation to the VOR, e.g. Paige and Busettini
Because the LVOR is commonly thought to keep the eyes stable during linear translation (reference), it also needs to scale with fixation depth. It is therefore possible that both the LVOR and self-motion perception use the same signal. While the fixation point in our experiment causes optokinetically driven eye movements to suplement the LVOR compensation, it is known that the LVOR only partially compensates for the amount of linear translation. If the same signal is also used for self-motion perception, one would expect that, the ratio of the expected LVOR compensation at 50 and 200cm reflect the ones presented in this paper (see \figref{p4:fig5} and \tabref{p4:tab2}).

It has been shown that the relative amount of compensation, or gain, depends on fixation distance angle \cite{paige1989, busettini1994,paige1998}. When fixating far away the gain is closer to 1 compared to fixations closer by. We extrapolated the gains found by Paige, 1989 to the 50 and 200cm fixation distances in our experiment and found gains of 0.50 and 0.68 respectively.

>>>>

\subsection{Relation to other studies}

@@

% Relation to the VOR
Because the function of the LVOR is to keep the eyes stable in the world during linear translation (reference), it also needs to scale with fixation depth \cite{paige1989, busettini1994,paige1998}. It is therefore possible that both the LVOR and self-motion perception use the same signal. Because of the visual fixation point, visual following mechanisms may augment the LVOR compensation. If the oculomotor signal generated by the LVOR is the same signal that is used for self-motion perception, one would expect that the LVOR compensation at 50 and 200cm closely relate to the corresponding oculomotor weights in the present study (see \figref{p4:fig5} and \tabref{p4:tab2}).

% WARNING, WE LOOK AT D200/D50 in the FIGURE!

We first computed the expected LVOR compensation based

The ratio of the 5.6 and 3.0 \textdegree LVOR compensation at the 50 and 200cm distances, as extrapolated from Paige \citeyear{1989}, is 1.87.

We took the LVOR compensation, as extrapolated from Paige \citeyear{paige1989}, at the 50 and 200cm distances and

We compared the gain found by Paige \citeyear{paige1989}

We extrapolated the gains found by Paige \citeyear{paige1989} to the 50 and 200cm fixation distances in our experiment and found gains of 0.50 and 0.68 respectively.

### 2015-02-08 src/paper4/p4_methods.tex
Minor updates

We fit \eqnref{p4:eq5} to the data using linear regression, finding one weight for every fixation depth (that is, $\alpha_{50}$ and $\alpha_{200}$) that minimizes the sum of squared errors ($\Sigma \epsilon^2$). Because these parameters can, in theory, contain both a depth-dependent and a depth-independent scaling, we compute their ratio, $\frac{\alpha_{50}}{\alpha_{200}}$, to remove any depth independent components. In case of perfect compensation, the expected ratio is $\frac{50}{200} = 1/4$, while in case of no depth-dependent scaling it is 1.

>>>>

We fit \eqnref{p4:eq5} to the data using linear regression, finding one weight for every fixation depth (that is, $\alpha_{50}$ and $\alpha_{200}$) that minimizes the sum of squared errors ($\Sigma \epsilon^2$). Because these parameters can, in theory, contain both a depth-dependent and a depth-independent scaling, we compute their ratio, $\frac{\alpha_{200}}{\alpha_{50}}$, to remove any depth independent components. In case of perfect compensation, the expected ratio is $\frac{200}{50} = 4$, while in case of no depth-dependent scaling it is 1.

### 2015-02-08 src/paper4/p4_results.tex
Minor updates

    \caption{\panelref{A} Actual (solid lines) and ideal (dashed lines) eye movement traces of one participant in the body-fixed (brown and orange) and world-fixed conditions (purple and pink). Gaze was directed at a near (brown and purple) or far (orange and pink) target. All traces shown are for 10m reference movements. \panelref{B} [Need to decide what to put here.]}
    \label{p4:fig2}
\end{figure}

@@

    \caption{Best-fit parameter values for 50 and 200 \si{\centi\metre} fixation distances, $\alpha_{50}$ and $\alpha_{200}$ respectively (see \eqnref{p4:eq5}), and their ratio, $\frac{\alpha_{200}}{\alpha_{50}} = \frac{d_{200}}{d_{50}}$, for each participant. Best-fit parameter values, $\alpha$, from our previous paper \protect\cite{clemens2015a} are included for reference.}

@@

	\caption{PSEs for all participants and the average \textpm SE. \panelref{A}  Body-fixed condition while fixation was either near (brown) or far (orange). \panelref{B} World-fixed condition while fixation was either near (purple) or far (pink).}
	\label{p4:fig4}
\end{figure}

@@

	\caption{}
	\label{p4:fig5}
\end{figure}

By examining the ratio of these weighting parameters, we remove any depth-independent contributions. In absence of  depth scaling, i.e. when $d_{50} = d_{200}$, the ratio should be one. For perfect compensation, that is when $d_{50} = 50  \wedge d_{200} = 200$, the ratio should be $1/4$. The actual ratio between $d_{50}$ and $d_{200}$ is plotted for each participant in \figref{p4:fig5}. While two participants show moderate compensation for depth, the majority of participants show no sign of scaling of eye movements by fixation distance. This is consistent with the observation that translations are perceived shorter with far compared to near fixations in the world condition.

>>>>

    \caption{\panelref{A} Actual (solid lines) and ideal (dashed lines) eye movement traces of one participant in the body-fixed (brown and orange) and world-fixed conditions (purple and pink). Gaze was directed at a near (brown and purple) or far (orange and pink) target. All traces shown are for 10m reference movements. \panelref{B} Normalized eye position for each participant (\textpm 95\% confidence interval) at the end of the translation interval for the near and far world fixed targets (purple and pink respectively) as well as the near and far body fixed fixation targets (brown and orange respectively). In addition, the average \textpm SE across all participants is shown. Zero indicates the eyes remained stationary relative to the body, and one indicates the eyes followed the near world fixed target perfectly.}
    \label{p4:fig2}
\end{figure}

@@

    \caption{Best-fit parameter values for 50 and 200 \si{\centi\metre} fixation distances, $\alpha_{50}$ and $\alpha_{200}$ respectively (see \eqnref{p4:eq5}), and their ratio, $\alpha_{200} / \alpha_{50} = d_{200} / d_{50}$, for each participant. Best-fit parameter values, $\alpha$, from our previous paper \protect\cite{clemens2015a} are included for reference.}

@@

	\caption{}
	\label{p4:fig4}
\end{figure}

@@

	\caption{Ratio between near and far parameter values, $\alpha_{200} / \alpha_{50} = d_{200} / d_{50}$ for every participant. Both perfect depth compensation, $\alpha_{200} / \alpha_{50} = 200 / 50 = 4$, as well as the lack thereof, $\alpha_{200} / \alpha{50} = 1$, are represented by a dashed line.}
	\label{p4:fig5}
\end{figure}

By examining the ratio of these weighting parameters, we remove any depth-independent contributions. In absence of  depth scaling, i.e. when $d_{50} = d_{200}$, the ratio should be one. For perfect compensation, that is when $d_{50} = 50  \wedge d_{200} = 200$, the ratio should be $4$. The actual ratio between $d_{50}$ and $d_{200}$ is plotted for each participant in \figref{p4:fig5}. While two participants show moderate compensation for depth, the majority of participants show no sign of scaling of eye movements by fixation distance. This is consistent with the observation that translations are perceived shorter with far compared to near fixations in the world condition.
